---
title: "2022 Mpox Multi-Jurisdictional Case-Control VE Public Health Evaluation"
subtitle: "Data Quality Checks & Preliminary Report"
authors: "Report by Case-Control Unit | VE Team | VTF | 2022 Multinational Monkeypox Response"
date: "`r format(Sys.time(), '%d %B %Y')`" 
output:
  html_document:
    code_folding: hide
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float: yes
    editor_options:
      chunk_output_type: console
      canonical: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = TRUE)
```

## Study objectives

**Primary:** Evaluate the effectiveness of the JYNNEOS vaccine in preventing symptomatic mpox disease among 18-49-year-old gay, bisexual, and other men who have sex with men, as well as transgender, non-binary, and gender-diverse persons.

**Secondary:** Estimate effectiveness by number of doses, route of administration and age group (if samples size allows).

## Resources:

-   Rmarkdown:

    -   [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/) (AOD: if you are familiar with R Markdown, then this is more digestible.)

    -   [Write Markdown in the RStudio Visual Editor](https://bookdown.org/yihui/rmarkdown-cookbook/rstudio-visual.html) (AOD: this is amazing!)

    -   [The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)

```{r libraries, message = FALSE, warning = FALSE}

# Data in: Pulled data directly from REDCap using API token
# Initial program date: 2022-12-15
# Last modified date: 2022-12-19

# Load packages --------------------------------
  pacman::p_load(here,         # file paths relative to R project root folder
                 tidyverse,    # data management and visualization
                 purrr,        # iteration
                 janitor,      # data management: cleaning and exploring data
                 lubridate,    # working with dates/epiweeks
                 naniar,       # Working with data structures, summaries, and visualizations for Missing Data
                 arsenal,      # provides unctions for large-scale statistical summaries
                 ggsci,        # scientific journal and sci-fi themed color palettes for 'ggplot2'
                 cowplot,       # streamlined plot theme and plot annotations for 'ggplot2'
                 knitr,
                 kableExtra,
                 DT,
                 stargazer,
                 plotly,
  )

# Helper (custom functions) ------------------------------------------------------------
#This function replicates the SAS proc freq function with the '/ list missing statement'. 
#Source: https://github.com/asnr/sas-to-r
pfreq = function(...) {
  dplyr::group_by(...) %>%
    dplyr::summarize(n = n()) %>%
    dplyr::mutate(pct= round(100 * n/sum(n), 1)) 
  #mutate(Percent=paste0(round(100 * n/sum(n), 1), "%")) 
}

# This function helps create consistent values for Yes/No variables.
# by reassigning '2' values a zero. 
give_two_a_zero <- function(x){
  x[x == 2 ] <- 0
  x
}


# Source data ---------------------------------------------------------------------

  source("~/GitHub/analysis_mpx-case-control/00_REDCap-API-linkage.R")

# Tidy data ----------------------------------------------------------------------
mpoxve <- raw %>%
    # Restrict to eligible participants (i.e., those that passed the eligibility screening)
    filter(inelig_stop ==  1) %>% 
    mutate(# Format all yes/no variables with 1(Yes)/2(No) values as 1(Yes)/0(No).
           across(contains(c("elig_age", "elig_gender_msm", "elig_sexual_partners",
                             "elig_healthcare", "first_dose_yesno", "second_dose_yesno",
                             "symptoms_yesno", "provider_dx", "clinic_yesno", "hospitalized",
                             "dose1_yesno", "dose2_yesno"), ignore.case = TRUE), give_two_a_zero),
           
           # Check the presence of a jurisdiction ID
           juris_detect = case_when(str_detect(pid, "CA_|CO_| CT_|DC_|GA_|LAC_|MD_|MN_|NYC_|NYS_|OR_|TN_") ~ 1,
                           TRUE ~ as.numeric(0)),
             #! On 2022-12-19, there was 9 records (1 in GA [#59] & 8 in TN) without a jurisdiction ID,
             #                 Oumar contacted TN in early December and GA on 2022-12-19 to append ID the next they share data.
             #                 NYC also experienced this issue have not uploaded data yet. TN has already addressed the issue.
             #                 Oumar shared TN's solution with GA and NYC. Before deleting records missing the TN code, Oumar 
             #                 archived the data here: 
             #                 (Case Control > Data management and analysis > data_archive > MultiJurisdictionalM_DATA_2022-12-19_1108). 
           
           # rename REDCap DAG variable
           jid = toupper(redcap_data_access_group),
           
           # Case Ascertainment: Symptomatic cases identified by state or local health departments who meet either
           #                     the confirmed or probable case definition will be eligible for inclusion. 
           #                     #! If a participant self-reports as a cases and the rest of their data
           #                        are consistent with being a case then we should follow-up with the
           #                        with he jurisdiction to confirm. We will likely include this participant as a case.
           
           # Flag those who reported having experienced mpox symptoms and specified one of the listed symptoms 
           symptom_type_complete = case_when(symptoms_yesno == 1 &
                                               (symptom_type___1 == 1 | symptom_type___2 == 1 | symptom_type___3 == 1 |
                                                  symptom_type___4 == 1 | symptom_type___5 == 1 | symptom_type___6 == 1 |
                                                  symptom_type___7 == 1 | symptom_type___8 == 1 | symptom_type___9 == 1 |
                                                  symptom_type___10 == 1 | symptom_type___11 == 1 | symptom_type___12 == 1 |
                                                  symptom_type___13 == 1 | symptom_type___14 == 1 | symptom_type___15 == 1 |
                                                  symptom_type___16 == 1) ~ 1,
                                                symptoms_yesno == 1 &
                                                  (symptom_type___1 == 1 & symptom_type___2 == 1 & symptom_type___3 == 1 &
                                                     symptom_type___4 == 1 & symptom_type___5 == 1 & symptom_type___6 == 1 &
                                                     symptom_type___7 == 1 & symptom_type___8 == 1 & symptom_type___9 == 1 &
                                                     symptom_type___10 == 1 & symptom_type___11 == 1 & symptom_type___12 == 1 &
                                                     symptom_type___13 == 1 & symptom_type___14 == 1 & symptom_type___15 == 1 &
                                                     symptom_type___16 == 1) ~ 0,
                                                TRUE ~ as.numeric(NA)),
           
           # Create variable for case/control classification by self- or site-report consistency checks. 
           ca_co = fct_relevel(as_factor(case_when(case_yesno %in% c(1,2) & provider_dx == 1 ~ "Case: self & site",
                                                   is.na(case_yesno)  & provider_dx == 1 ~ "Case: self but site missing",
                                                   case_yesno == 3 & provider_dx == 0 ~ "Control: self & site",
                                                   is.na(case_yesno)  & provider_dx == 0 ~ "Control: self but site missing",
                                                   case_yesno %in% c(1,2) & provider_dx == 0 ~ "Discrepancy: site case",
                                                   case_yesno == 3 & provider_dx == 1 ~ "Discrepancy: self case",
                                                   TRUE ~ as.character(NA))),
                              "Case: self & site", "Case: self but site missing",
                              "Control: self & site", "Control: self but site missing",
                              "Discrepancy: site case", "Discrepancy: self case"),
           
           # Flag cases with/without symptoms; Everyone who said that they had mpox symptoms, specified at least one of the options.
           ca_co_symp = fct_relevel(as_factor(case_when(ca_co %in% c("Case: self & site", "Case: self but site missing") &
                                                          symptoms_yesno == 1  ~ "Case: symptom +",
                                                        ca_co %in% c("Case: self & site", "Case: self but site missing") &
                                                          symptoms_yesno == 0  ~ "Case: symptom -",
                                                        ca_co %in% c("Control: self & site", "Control: self but site missing") ~ "Control",
                                                TRUE ~ as.character(NA))),
                                    "Case: symptom +", "Case: symptom -",
                                    "Control"),
           
           # Format all date variables as YYYY-MM-DD
           across(contains("_date", ignore.case = TRUE), ymd),
           
           # Flag mpox symptoms date within 2022-08-15 and system date. 
              #! Note that I am using Aug 15, rather Aug 19 per the protocol because
              #! jurisdictions have report discrepancies between the self-reported symptoms date
              #! on the survey versus clinic records. 
           timepoint_interval <- interval(ymd("2022-08-15"), ymd(Sys.Date())),
           symp_clinic_date_met = case_when((symptoms_date %within% timepoint_interval) |
                                              (clinic_date %within% timepoint_interval) ~ 1,
                                            TRUE ~ as.numeric(0))
            ) %>% 
    select(pid, jid, everything(), -redcap_data_access_group)


```


