---
title: "MMWR Clearance & Reviewer Responses" 
subtitle: "2022 Mpox Multi-Jurisdictional Case-Control VE Public Health Evaluation"
author: "Report by Case-Control Unit | VE Team | VTF | 2022 Multinational Monkeypox Response"
date: "`r format(Sys.time(), '%d %B %Y')`" 
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
  # html_document:
    code_folding: hide
    highlight: tango
    #toc: yes
    toc_depth: 3
    #toc_float: yes
    editor_options:
      chunk_output_type: console
      canonical: true
      
    # word_document:
    # reference_docx: "template.docx"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## **Report objectives**

1.  Output distribution of immunocompromising conditions and CD4 count category.

2.  Output distribution of immunocompromising conditions.

```{r libraries, message = FALSE, warning = FALSE}


# Load packages --------------------------------
  pacman::p_load(here,        # file paths relative to R project root folder
                 rio,         # import/export
                 readxl,      # read excel files
                 tidyverse,   # data management and visualization
                 purrr,       # iteration
                 stringr,     # manipulate text strings 
                 janitor,     # data management: cleaning and exploring data
                 data.table,  # Provides a high-performance version of base R's data.frame
                 lubridate,   # working with dates/epiweeks
                 naniar,      # Working with data structures, summaries, and visualizations for Missing Data
                 arsenal,     # provides unctions for large-scale statistical summaries
                 knitr,       # Provides a general-purpose tool for dynamic report generation in R
                 kableExtra,  # simplifies the way to manipulate the HTML or 'LaTeX' codes generated by 'kable()
                 DT,          # provides an R interface to the JavaScript library DataTables
                 gtsummary,   # publication-ready analytical and summary tables
                 tableone,    # Creates 'Table 1', i.e., description of baseline patient characteristics
                 stargazer,   # provides a way to create publication quality tables
                 survival,    # conditional logistic regression
                 sjplot,      # output model result HTML
                 modelr,      # Provides functions that help you create elegant pipelines when modelling
                 broom,       # tidy up results from regressions
                 lmtest,      # likelihood-ratio tests
                 parameters,  # alternative to tidy up results from regressions
                 see,         # alternative to visualise forest plots
                 easystats,
                 ggsci,       # scientific journal and sci-fi themed color palettes for 'ggplot2'
                 cowplot     # streamlined plot theme and plot annotations for 'ggplot2'

                 
  )

# Global option number format
  options(scipen = 9999)

#GT Table Theme
  theme_gtsummary_journal(journal = "jama")
  theme_gtsummary_compact()
  
# Helper (custom functions) ------------------------------------------------------------
#This function replicates the SAS proc freq function with the '/ list missing statement'. 
#Source: https://github.com/asnr/sas-to-r
pfreq = function(...) {
  dplyr::group_by(...) %>%
    dplyr::summarize(n = n()) %>%
    dplyr::mutate(pct= round(100 * n/sum(n), 1)) 
  #mutate(Percent=paste0(round(100 * n/sum(n), 1), "%")) 
}


# Load analysis dataset and output template  -------------------------------------------

  # The results shared with co-authors were generated from these data 
    mpoxve_shared_mmwr <- here("data","analysis_mpoxve_mmwr_2023-03-31.RDS") %>%
      read_rds()
  
  # Updated data (Friday 2023-04-14) 
    mpoxve <- here("data","analysis_mpoxve_mmwr.RDS") %>%
      read_rds()
  
 
```

## **Output breakdown of Matching for California EIP participants.**

```{r}



mpoxve_shared_mmwr %>% 
  filter(model == "Main" & match_ratio == "1 case:4 controls") %>% 
  select(jid, minset_vars) %>% 
  tbl_summary(
    by = jid,
    label = list(minset_vars ~ "Min data elements")
  )  %>% 
  add_n() %>% 
  add_overall() %>% 
  bold_labels()

tt <- mpoxve %>% 
  filter(model == "Main" & match_ratio == "None" & jid == "CA") %>% 
  select(pid, jid, )

```

## **Distribution of immunocompromising conditions**

**Table 1. Distribution of respondents with a minimum set of data elements**

```{r}
mpoxve %>% 
  filter(model == "Main" & match_ratio == "1 case:4 controls") %>%
  filter(minset_vars == "Complete") %>%
  filter( hiv_status_cat == "Living with HIV") %>%
  select(caco, hiv_cd4_cat) %>%
  tbl_summary(
    by = caco,
        label = list(hiv_cd4_cat ~ "CD4 count\U1d43"),
    missing_text = "Missing"
  )  %>%
  add_n() %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt()%>%
  gt::tab_source_note(gt::md("\U1d43 Denominator is those living with HIV." ))

# 
# mpoxve %>% 
#   filter(model == "Main" & match_ratio == "1 case:4 controls") %>%
#   filter(minset_vars == "Complete") %>%
#   filter( hiv_status_cat == "Living with HIV") %>% 
#   select(caco, hiv_status_cat, hiv_cd4_cat, immune_response_cat,
#          immunocompromised) %>%
#   tbl_summary(
#     by = caco,
#         label = list(hiv_cd4_cat ~ "CD4 count\U1d47",
#                  immune_response_cat ~ "Non-HIV immunocompromising conditions",
#                  immunocompromised ~ "Immunocompromising conditions\U1d9c"),
#     missing_text = "Missing"
#   )  %>%
#   add_n() %>%
#   add_overall() %>%
#   bold_labels() %>%
#   as_gt()%>%
#   gt::tab_source_note(gt::md("\U1d43 Most missing are coming from CA (n=30)."))%>%
#   gt::tab_source_note(gt::md("\U1d47 Denominator is those living with HIV." )) %>%
#   gt::tab_source_note(gt::md("\U1d9c HIV or any medical condition other than HIV that weakens your immune response, or use of medicine (other than for HIV) that weakens immune response"))

# tt <-mpoxve %>% 
#   filter(model == "Main" & match_ratio == "1 case:4 controls") %>%
#   filter(minset_vars == "Complete") %>%  
#   pfreq(jid, hiv_status_cat)

```

**Figure 1. Missingness patterns across the set of minimum data elements (incomplete)**


```{r}
mpoxve %>% 
  filter(minset_vars == "Incomplete") %>%
  select(case_yesno, index_date, vax1_yesno, vax1_date, vax2_yesno, vax2_date)%>%
  gg_miss_upset()

# tt <- mpoxve %>% 
#   filter(minset_vars == "Incomplete") %>%
#   filter(jid != "TN")%>%
#   # filter(pid == "GA_73")%>%
#   select(minset_vars, pid, caco_stat_cat, case_yesno, index_date, test_result_date, provider_dx, symptoms_date,
#          clinic_date, control_visit_date,
#          vax1_yesno, dose1_yesno, first_dose_yesno, vax1_date, dose1_date,first_dose_date, 
#          vax2_yesno, dose2_yesno, second_dose_yesno, vax2_date, dose2_date, second_dose_date) %>% 
#   arrange(pid)
#   
# clipr::write_clip(tt)

```

## **Descriptive statistics: population with complete set of minimum data elements**

**Table 2. Participant characteristics by case status**

```{r}
mpoxve %>%
  filter(minset_vars == "Complete") %>%
  select(caco, sid, age_cat, race_ethn_cat, elig_gender_cat, health_ins_cat,
         housing_cat, sex_work_cat, hiv_status_cat, hiv_cd4_cat, hiv_prep_cat,
         immunocompromised, close_contact_dx_cat, sex_part_num_cat) %>%
  tbl_summary(
    by = caco,
        label = list(sid ~ "Jurisdiction-States",
                 age_cat ~ "Age categories",
                 race_ethn_cat ~ "Ethnicity, race\U1d43",
                 elig_gender_cat ~ "Gender",
                 health_ins_cat ~ "Insurance Status",
                 housing_cat ~ "Experienced homelessness in past 3 weeks",
                 sex_work_cat ~ "Transactional sex",
                 hiv_status_cat ~ "HIV status",
                 hiv_cd4_cat ~ "CD4 count\U1d47",
                 hiv_prep_cat ~ "HIV PrEP\U1d9c",
                 immunocompromised ~ "Immunocompromised\U1d48",
                 sex_part_num_cat ~ "Number of sexual partners",
                 close_contact_dx_cat ~ "Close contact w/mpox case"),
    missing_text = "Missing"
  )  %>%
  add_n() %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt()%>%
  gt::tab_source_note(gt::md("\U1d43 Hispanic includes self-reported as Hispanic regardless of race.")) %>%
  gt::tab_source_note(gt::md("\U1d47 Denominator is those living with HIV." )) %>%
  gt::tab_source_note(gt::md("\U1d9c Denominator is those who report anything other than living with HIV."))%>%
  gt::tab_source_note(gt::md("\U1d48 HIV or any medical condition other than HIV that weakens your immune response, or use of medicine (other than for HIV) that weakens immune response"))

```

**Table 3. Participant characteristics by vaccination status as defined for the main model** *Note* The N decreased in this table because we drop s3 and s5 from vaccination status variable in the main model.

```{r}
mpoxve %>%
  filter(minset_vars == "Complete") %>%
  select(vax_stat_ve_main, sid, age_cat, race_ethn_cat, elig_gender_cat, health_ins_cat,
         housing_cat, sex_work_cat, hiv_status_cat, hiv_cd4_cat, hiv_prep_cat,
         immunocompromised, close_contact_dx_cat, sex_part_num_cat) %>%
  tbl_summary(
    by = vax_stat_ve_main,
    label = list(sid ~ "Jurisdiction-States",
                 age_cat ~ "Age categories",
                 race_ethn_cat ~ "Ethnicity, race\U1d43",
                 elig_gender_cat ~ "Gender",
                 health_ins_cat ~ "Insurance Status",
                 housing_cat ~ "Experienced homelessness in past 3 weeks",
                 sex_work_cat ~ "Transactional sex",
                 hiv_status_cat ~ "HIV status",
                 hiv_cd4_cat ~ "CD4 count\U1d47",
                 hiv_prep_cat ~ "HIV PrEP\U1d9c",
                 immunocompromised ~ "Immunocompromised\U1d48",
                 sex_part_num_cat ~ "Number of sexual partners",
                 close_contact_dx_cat ~ "Close contact w/mpox case"),
    missing_text = "Missing"
  )  %>%
  add_n() %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt()%>%
  gt::tab_source_note(gt::md("\U1d43 Hispanic includes self-reported as Hispanic regardless of race.")) %>%
  gt::tab_source_note(gt::md("\U1d47 Denominator is those living with HIV." )) %>%
  gt::tab_source_note(gt::md("\U1d9c Denominator is those who report anything other than living with HIV."))%>%
  gt::tab_source_note(gt::md("\U1d48 HIV or any medical condition other than HIV that weakens your immune response, or use of medicine (other than for HIV) that weakens immune response"))

```

## **Case and control matching by state and within 4-weeks of index event (IE) date**

<!-- **Figure 2. Missingness patterns across the set of minimum data elements (incomplete)** -->


<!-- ```{r} -->
<!-- mpoxve_mod_na <- mpoxve %>% -->
<!--   filter(minset_vars == "Complete") %>% -->
<!--   filter(sid == "MD" & !is.na(vax_stat_ve_main)) %>%  -->
<!--   select(sid, jid, pid, caco, vax_stat_ve_main, vax_stat_post_acip, age, race_ethn, immunocompromised, -->
<!--          close_contact_dx_cat) -->

<!-- gg_miss_var(mpoxve_mod_na, facet = jid) -->



<!-- ``` -->

**Table 4. Distribution of cases and controls relative complete case data after matching (1 case:up to 4 controls)**

```{r}

#https://stackoverflow.com/questions/75185184/matching-controls-and-cases-using-some-conditions


#set seed  ------------------
set.seed(20230320)


# subset dataset I will use  ------------------
mpoxve_main <- mpoxve %>% 
  filter(minset_vars == "Complete")  %>%
  select(pid, caco, sid, age, age_cat, race_ethn_cat, race_ethn, elig_gender_cat,
         health_ins_cat, housing_cat, sex_work_cat, hiv_status_cat, hiv_cd4_cat,
         hiv_prep_cat, immunocompromised, close_contact_dx_cat, sex_part_num_cat, vax_stat_post_acip,
         vax_stat_ve_main, vax_stat_ve_s6full, vax_stat_ve_s6excl, index_date,
         index_yrmo, index_epiyrwk_4) %>% 
  drop_na(caco, vax_stat_ve_main, age, race_ethn, immunocompromised,
         close_contact_dx_cat, vax_stat_ve_main, vax_stat_ve_s6full)


mpoxve_s6excl <- mpoxve %>% 
  filter(minset_vars == "Complete")  %>%
  select(pid, caco, sid, age, age_cat, race_ethn_cat, race_ethn, elig_gender_cat,
         health_ins_cat, housing_cat, sex_work_cat, hiv_status_cat, hiv_cd4_cat,
         hiv_prep_cat, immunocompromised, close_contact_dx_cat, sex_part_num_cat, vax_stat_post_acip,
         vax_stat_ve_main, vax_stat_ve_s6full, vax_stat_ve_s6excl, index_date,
         index_yrmo, index_epiyrwk_4) %>% 
  drop_na(caco, vax_stat_ve_main, age, race_ethn, immunocompromised,
         close_contact_dx_cat, vax_stat_ve_s6excl)

# output matched dataset for 1:2 ratio ------------------

  # IE (caliper)  & State (Exact)
  m_data_r2 <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 2),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:2",
           match_vars = "State & IE",
           mod = "Main")
  
  # IE (caliper)
  m_data_r2_ie <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 #exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 2),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:2",
           match_vars = "IE",
           mod = "Main")

# output match dataset for 1:3 ratio ------------------
  # IE (caliper)  & State (Exact)
  m_data_r3 <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 3),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:3",
           match_vars = "State & IE",
           mod = "Main")
  
  # IE (caliper)
  m_data_r3_ie <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 #exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 3),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:3",
           match_vars = "IE",
           mod = "Main")
  

# output match dataset for 1:4 ratio: main model & s6 full vaccinated ------------
  
  # IE (caliper)  & State (Exact)
  m_data_r4 <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 4),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:4",
           match_vars = "State & IE",
           mod = "Main")

  # IE (caliper)
  m_data_r4_ie <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_main,
                                 #exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 4),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:4",
           match_vars = "IE",
           mod = "Main")

  
# output match dataset for 1:4 ratio: main model & s6 excluded ------------
  
  # IE (caliper)  & State (Exact)
  m_data_r4_s6excl <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_s6excl,
                                 exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 4),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:4",
           match_vars = "State & IE",
           mod = "s6excl")

  # IE (caliper)
  m_data_r4_ie_s6excl <- match.data(matchit(I(caco == "Case") ~ index_date, 
                                 data = mpoxve_s6excl,
                                 #exact = ~ sid,
                                 caliper = c(index_date = 28), std.caliper = FALSE,
                                 distance = "euclidean", ratio = 4),
                          subclass = "matched_id") %>% 
    mutate(ratio = "1:4",
           match_vars = "IE",
           mod = "s6excl")

# Flag exact match IDs ------------------

  subclass_2 <- levels(m_data_r2$matched_id)[table(m_data_r2$matched_id) == 3]
  m_data_r2_exact <- m_data_r2[m_data_r2$matched_id %in% subclass_2,]%>% 
    mutate(r_exact = 1)
  
  subclass_3 <- levels(m_data_r3$matched_id)[table(m_data_r3$matched_id) == 4]
  m_data_r3_exact <- m_data_r3[m_data_r3$matched_id %in% subclass_3,] %>% 
    mutate(r_exact = 1)
  
  subclass_4 <- levels(m_data_r4$matched_id)[table(m_data_r4$matched_id) == 5]
  m_data_r4_exact <- m_data_r4[m_data_r4$matched_id %in% subclass_4,]%>% 
    mutate(r_exact = 1)
  
  subclass_4_s6excl  <- levels(m_data_r4_s6excl$matched_id)[table(m_data_r4_s6excl$matched_id) == 5]
  m_data_r4_exact_s6excl <- m_data_r4_s6excl[m_data_r4_s6excl$matched_id %in% subclass_4_s6excl,]%>% 
    mutate(r_exact = 1)
  
  
  subclass_2_ie <- levels(m_data_r2_ie$matched_id)[table(m_data_r2_ie$matched_id) == 3]
  m_data_r2_exact_ie <- m_data_r2_ie[m_data_r2_ie$matched_id %in% subclass_2,]%>% 
    mutate(r_exact = 1)
  
  subclass_3_ie <- levels(m_data_r3_ie$matched_id)[table(m_data_r3_ie$matched_id) == 4]
  m_data_r3_exact_ie <- m_data_r3_ie[m_data_r3_ie$matched_id %in% subclass_3_ie,]%>% 
    mutate(r_exact = 1)
  
  
  subclass_4_ie <- levels(m_data_r4_ie$matched_id)[table(m_data_r4_ie$matched_id) == 5]
  m_data_r4_exact_ie <- m_data_r4_ie[m_data_r4_ie$matched_id %in% subclass_4_ie,]%>% 
    mutate(r_exact = 1)
  
  subclass_4_ie_s6excl <- levels(m_data_r4_ie_s6excl$matched_id)[table(m_data_r4_ie_s6excl$matched_id) == 5]
  m_data_r4_exact_ie_s6excl <- m_data_r4_ie_s6excl[m_data_r4_ie_s6excl$matched_id %in% subclass_4_ie_s6excl,]%>% 
    mutate(r_exact = 1)

# combine the data ----------------------------------
  
 mpoxve_matched <-  mpoxve_main %>% 
    mutate(ratio = "None",
           match_vars = "None",
           mod = "Main") %>% 
    bind_rows((mpoxve_s6excl %>% 
                 mutate(ratio = "None",
                        match_vars = "None",
                        mod = "s6excl")),
              m_data_r2, m_data_r2_ie, 
              m_data_r3, m_data_r3_ie, 
              m_data_r4, m_data_r4_ie,
              m_data_r4_s6excl, m_data_r4_ie_s6excl) %>%
    mutate(ratio = fct_inorder(as_factor(ratio)),
           match_vars = fct_inorder(as_factor(match_vars)),
           mod = fct_inorder(as_factor(mod)),
           r_exact = case_when((mod ==  "Main" & ratio == "1:2" &
                                 match_vars == "State & IE" &
                                 matched_id %in% subclass_2) |
                                 (mod ==  "Main" & ratio == "1:2" &
                                 match_vars == "IE" &
                                 matched_id %in% subclass_2_ie) |
                                 (mod ==  "Main" & ratio == "1:3" &
                                 match_vars == "State & IE" &
                                 matched_id %in% subclass_3)|
                                 (mod ==  "Main" & ratio == "1:3" &
                                 match_vars == "IE" &
                                 matched_id %in% subclass_3_ie)|
                                 (mod ==  "Main" & ratio == "1:4" &
                                 match_vars == "State & IE" &
                                 matched_id %in% subclass_4)|
                                 (mod ==  "Main" & ratio == "1:4" &
                                 match_vars == "IE" &
                                 matched_id %in% subclass_4_ie)|
                                 (mod ==  "s6excl" & ratio == "1:4" &
                                 match_vars == "State & IE" &
                                 matched_id %in% subclass_4_s6excl)|
                                 (mod ==  "s6excl" & ratio == "1:4" &
                                 match_vars == "IE" &
                                 matched_id %in% subclass_4_ie_s6excl) ~ 1,
                               TRUE ~ as.numeric(0))) %>% 
    select(mod, ratio, match_vars, r_exact, pid, caco, matched_id, weights, index_date, sid, everything()) %>% 
    arrange(mod, ratio, match_vars, matched_id, caco)
  
  # clipr::write_clip(mpoxve_matched)

# combine counts ----------------------------------

r_upto<- mpoxve_matched %>%
    pfreq(mod, ratio, match_vars, caco) %>%
    mutate(match_data = case_when(ratio == "None" ~ "None",
                                  TRUE ~ as.character("Upto")))

r_exact <- mpoxve_matched %>%
  filter(r_exact == 1) %>% 
  pfreq(mod, ratio, match_vars, caco) %>%
  mutate(match_data = "Exact")
    
caco_match_counts <- bind_rows(r_upto, r_exact) %>% 
  select(mod, ratio, match_vars, match_data, everything()) %>% 
  mutate(match_data = fct_relevel(as_factor(match_data),
                                  "None", "Exact", "Upto"),
         mod_ratio_vars_data = fct_relevel(as_factor(str_c(mod, ratio, 
                                                           match_vars, match_data, sep = "_")))) %>% 
  arrange(mod_ratio_vars_data, caco) %>% 
  select(-mod_ratio_vars_data)

caco_match_counts_r <- caco_match_counts %>%
  filter(ratio!= "None") %>% 
  full_join((caco_match_counts %>%
               filter(ratio== "None") %>% 
               ungroup() %>% 
               rename(tot = n) %>% 
               select(mod, caco, tot)), 
            by = c("mod", "caco")) %>% 
  mutate(pct_tot = round(100*(n/tot), 1)) %>% 
  filter(ratio == "1:4" & match_vars == "State & IE" & match_data == "Upto") %>% 
  ungroup() %>% 
  select(mod, caco, n, tot, pct_tot) %>% 
  mutate(mod = case_when(mod == "Main" ~ " M1-S6 partial &\nM2-S6 full",
                         TRUE ~ as.character("M2-S6 excl"))) %>% 
  rename(Model = mod, `Case status` = caco, 
         `N matched` = n, `N complete` =  tot,
         Percent = pct_tot)


caco_match_counts_r %>% 
  DT::datatable(., extensions='Buttons',
                     options = list(
                       searching = T,
                       pageLength = 10,
                       dom = 'Bfrtip',
                       buttons = c('csv')))


  # clipr::write_clip(caco_match_counts)


```

## **Descriptive statistics of matched study population** 

**Table 5. Characteristics by case status**

```{r}

mpoxve_matched %>%
  filter(mod == "Main" & ratio == "1:4" & match_vars == "State & IE") %>%
    select(caco, sid, age_cat, race_ethn_cat, elig_gender_cat, health_ins_cat,
         housing_cat, sex_work_cat, hiv_status_cat, hiv_cd4_cat, hiv_prep_cat,
         immunocompromised, close_contact_dx_cat, sex_part_num_cat,
         vax_stat_ve_main, vax_stat_ve_s6full, vax_stat_ve_s6excl) %>%
  tbl_summary(
    by = caco,
        label = list(sid ~ "Jurisdiction-States",
                 age_cat ~ "Age categories",
                 race_ethn_cat ~ "Ethnicity, race\U1d43",
                 elig_gender_cat ~ "Gender",
                 health_ins_cat ~ "Insurance Status",
                 housing_cat ~ "Experienced homelessness in past 3 weeks",
                 sex_work_cat ~ "Transactional sex",
                 hiv_status_cat ~ "HIV status",
                 hiv_cd4_cat ~ "CD4 count\U1d47",
                 hiv_prep_cat ~ "HIV PrEP\U1d9c",
                 immunocompromised ~ "Immunocompromised\U1d48",
                 sex_part_num_cat ~ "Number of sexual partners",
                 close_contact_dx_cat ~ "Close contact w/mpox case",
                 vax_stat_ve_main ~ "Vax status: M1-S6 partial\U1d49",
                 vax_stat_ve_s6full ~ "Vax status: M2-S6 full\U1d49",
                 vax_stat_ve_s6excl ~ "Vax status: M3-S6 excl\U1DA0"),
    missing_text = "Missing"
  )  %>%
  add_n() %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt()%>%
  gt::tab_source_note(gt::md("\U1d43 Hispanic includes self-reported as Hispanic regardless of race.")) %>%
  gt::tab_source_note(gt::md("\U1d47 Denominator is those living with HIV." )) %>%
  gt::tab_source_note(gt::md("\U1d9c Denominator is those who report anything other than living with HIV."))%>%
  gt::tab_source_note(gt::md("\U1d48 HIV or any medical condition other than HIV that weakens your immune response, or use of medicine (other than for HIV) that weakens immune response"))%>%
  gt::tab_source_note(gt::md("\U1d49 S6: D1 is > 13 d before IE & D1 is ≥ 24 d before D2 & D2 is ≤ 13 d before IE"))%>%
  gt::tab_source_note(gt::md("\U1DA0 Missing represent scenarios 6."))

```

## **Model 1 results**

```{r}

analysis_main <- mpoxve_matched %>%
  filter(mod == "Main" & ratio == "1:4" & match_vars == "State & IE") %>%
  mutate(caco = case_when(caco == "Control" ~ 0,
                          TRUE ~ as.numeric(1)),
         vax_stat_ve_main = fct_rev(vax_stat_ve_main),
         vax_stat_ve_s6full = fct_rev(vax_stat_ve_s6full))


mod1_unadj_main <- clogit(caco ~ vax_stat_ve_main,
                          strata(matched_id),
                          data = analysis_main)

mod1_adj_main <- clogit(caco ~ vax_stat_ve_main + age + race_ethn +  immunocompromised +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_main)

```

**Crude: left OR VS. adjusted (age, race, immunocompromised & close contacts): right OR**

```{r}

tab_model(mod1_unadj_main, mod1_adj_main, show.aic = T, show.obs = T)

```

## **Model 1 vs 2 results**

```{r}

mod2_unadj_s6full <- clogit(caco ~ vax_stat_ve_s6full,
                          strata(matched_id),
                          data = analysis_main)

mod2_adj_s6full <- clogit(caco ~ vax_stat_ve_s6full + age + race_ethn +  immunocompromised +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_main)

```

**Crude -- model 1: left OR VS. model 2: right OR**

```{r}

tab_model(mod1_unadj_main, mod2_unadj_s6full, show.aic = T, show.obs = T)

```

**Adjusted -- model 1: left OR VS. model 2: right OR**

```{r}

tab_model(mod1_adj_main, mod2_adj_s6full, show.aic = T, show.obs = T)

```

## **Model 1 vs 2 vs 3 results**

```{r}


analysis_s6excl <- mpoxve_matched %>%
  filter(mod == "s6excl" & ratio == "1:4" & match_vars == "State & IE") %>%
  mutate(caco = case_when(caco == "Control" ~ 0,
                          TRUE ~ as.numeric(1)),
         vax_stat_ve_main = fct_rev(vax_stat_ve_main),
         vax_stat_ve_s6full = fct_rev(vax_stat_ve_s6full),
         vax_stat_ve_s6excl = fct_rev(vax_stat_ve_s6excl))

# model 1
mod1_unadj_main <- clogit(caco ~ vax_stat_ve_main,
                          strata(matched_id),
                          data = analysis_s6excl)

mod1_adj_main <- clogit(caco ~ vax_stat_ve_main + age + race_ethn +  immunocompromised +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_s6excl)

# model 2
mod2_unadj_s6full <- clogit(caco ~ vax_stat_ve_s6full,
                          strata(matched_id),
                          data = analysis_s6excl)

mod2_adj_s6full <- clogit(caco ~ vax_stat_ve_s6full + age + race_ethn +  immunocompromised +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_s6excl)


# model 3
mod3_unadj_s6excl <- clogit(caco ~ vax_stat_ve_s6excl,
                          strata(matched_id),
                          data = analysis_s6excl)

mod3_adj_s6excl <- clogit(caco ~ vax_stat_ve_s6excl + age + race_ethn +  immunocompromised +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_s6excl)

```

**Crude -- model 1: left OR VS. model 2: middle OR VS. model 3: right OR**

```{r}

tab_model(mod1_unadj_main, mod2_unadj_s6full, mod3_unadj_s6excl, show.aic = T, show.obs = T)

```

**Adjusted -- model 1: left OR VS. model 2: middle OR VS. model 3: right OR**

```{r}

tab_model(mod1_adj_main, mod2_adj_s6full, mod3_adj_s6excl, show.aic = T, show.obs = T)

```

## **Model 1 results by immunocompromised status**

```{r}

analysis_main <- mpoxve_matched %>%
  filter(mod == "Main" & ratio == "1:4" & match_vars == "State & IE") %>%
  mutate(caco = case_when(caco == "Control" ~ 0,
                          TRUE ~ as.numeric(1)),
         vax_stat_ve_main = fct_rev(vax_stat_ve_main),
         vax_stat_ve_s6full = fct_rev(vax_stat_ve_s6full))

analysis_ic_yes <- analysis_main %>% 
  filter(immunocompromised == "Yes")

analysis_ic_no <- analysis_main %>% 
  filter(immunocompromised == "No")

mod1_adj_main_ic_yes <- clogit(caco ~ vax_stat_ve_main + age + race_ethn +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_ic_yes)

mod1_adj_main_ic_no <- clogit(caco ~ vax_stat_ve_main + age + race_ethn +
                            close_contact_dx_cat,
                          strata(matched_id),
                          data = analysis_ic_no)

```

**IC-Yes (left-side OR), IC-No (right-side OR)**

```{r}

tab_model(mod1_adj_main_ic_yes, mod1_adj_main_ic_no, show.aic = T, show.obs = T)

```

## **Next steps**

1.  Explore why respondents with D2 are being excluded because of missing D2 dates

2.  Clean route of administration and output model 1 results stratified by route of administration
